On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-10-10 paper/paper.tex
Reviewer typo fixes

\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.
% Say why it is an interesting problem
  However, capturing traditional control flow in an deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilities of
  Haskell-based deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languages can be cleaner, Haskell-idiomatic,
  and more declarative in nature.

@@

example' :: E Int
example' = CaseExp (LeftExp 'a') (SumMatchExp
  (OneProdMatch (Lam 1 (Ord (Var 1))))
  (OneSumMatch (OneProdMatch (Lam 2 (Var 2)))))

@@

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given a representation in terms of \ttt{Either}, \ttt{(,)}, \ttt{()}
and \ttt{Void}.  This "standardized" type representation is given by \ttt{ERepTy
T}. \ttt{ERepTy} is an type family associated to the type class \ttt{ERep}. This
type will be called the \textit{canonical type} of \ttt{T}.

@@

\section{Representing pattern matches}
\label{sec:PatRep}

>>>>

\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.
% Say why it is an interesting problem
  However, capturing traditional control flow in a deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilities of
  Haskell-based deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languages can be cleaner, Haskell-idiomatic,
  and more declarative in nature.

@@

example' :: E Int
example' = CaseExp (LeftExp (CharLit 'a'))
  (SumMatchExp
    (OneProdMatch (Lam 1 (Ord (Var 1))))
    (OneSumMatch (OneProdMatch (Lam 2 (Var 2)))))

@@

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given a representation in terms of \ttt{Either}, \ttt{(,)}, \ttt{()}
and \ttt{Void}.  This "standardized" type representation is given by \ttt{ERepTy
T}. \ttt{ERepTy} is a type family associated to the type class \ttt{ERep}. This
type will be called the \textit{canonical type} of \ttt{T}.

@@

\section{Representing pattern matching}
\label{sec:PatRep}
